---
title: "More ggplot Figures Peer Review"
output: html_document
---

# PUT YOUR NAME HERE

## Problem 1

Create the figure in the solution for Problem 1, using the data included in the R Markdown file.

```{r problem_1_data,include=FALSE}

#####DO NOT MODIFY THIS CHUNK
library(tidyverse)

set.seed(12345)
var1<-runif(50,0,10)
set.seed(12345)
var2<-var1+rnorm(50,5,2)
set.seed(12345)
var3<- var1*(-rnorm(50,1,.2))

dat1<-tibble(var1,var2,var3)


```


####Make sure you install any necessary libraries
```{r problem_1, echo=FALSE, message=FALSE}
# Create the plot
ggplot(dat1, aes(x = var1, y = var2)) +
  geom_point(color = "black") + # Scatter plot
  geom_smooth(method = "loess", color = "blue", fill = "gray", alpha = 0.4) + # Smoothed line with confidence interval
  labs(x = "Variable1", y = "Variable2") + # Axis labels
  theme_minimal() # Clean theme
####PUT YOUR CODE HERE
```

## Problem 2

Create the figure in the solution for Problem 2, using the data included in the R Markdown file.

```{r problem_2_data,include=FALSE}

#####DO NOT MODIFY THIS CHUNK

set.seed(10)
var1<-runif(50,0,10)
set.seed(10)
var2<-var1+rnorm(50,5,2)
set.seed(10)
var3<- var1*(-rnorm(50,1,.2))

dat2<-tibble(var1,var2,var3)
```


```{r solution_p2,echo=FALSE,message=FALSE}

library(GGally)

# Create the pair plot with correlation values
ggpairs(dat2, 
        upper = list(continuous = wrap("cor", size = 6, color = "blue")),  # Display correlations
        lower = list(continuous = wrap("points", color = "orange")),        # Scatter plot
        diag = list(continuous = wrap("densityDiag", fill = "blue")),        # Density plot
        axisLabels = "show")  # Display axis labels


```

## Problem 3

Create the figure in the solution for Problem 3, using the data included in the R Markdown file.

```{r problem_3_data,include=FALSE}

#####DO NOT MODIFY THIS CHUNK

set.seed(12)
var1<-runif(50,0,10)
set.seed(12)
var2<-var1+rnorm(50,5,2)
set.seed(12)
var3<- var1*(-rnorm(50,1,.2))

dat3<-tibble(var1,var2,var3)
```

```{r problem3,echo=FALSE}

# Compute the correlation matrix
corr_matrix <- cor(dat3)

# Convert the correlation matrix to a tidy format for ggplot2
corr_data <- as.data.frame(as.table(corr_matrix))

# Filter out the diagonal elements (self-correlations)
corr_data <- corr_data[corr_data$Var1 != corr_data$Var2, ]

# Create the heatmap plot with the correct axis configuration
ggplot(corr_data, aes(Var1, Var2, fill = Freq)) +
  geom_tile() +
  scale_fill_gradient2(low = "blue", high = "red", mid = "white", midpoint = 0) + 
  labs(x = "Variables", y = "Variables", fill = "Corr") +
  theme_minimal() +
  theme(
    axis.text.x = element_text(angle = 45, hjust = 1),  # Rotate x-axis labels for better readability
    axis.text.y = element_text(size = 12),  # Adjust y-axis text size
    axis.title = element_text(size = 14)  # Increase axis title size for clarity
  ) +
  scale_x_discrete(limits = c("var2", "var3")) + # Set x-axis order
  scale_y_discrete(limits = c("var1", "var2"))  # Set y-axis order
```

## Problem 4

Create the figure in the solution for Problem 4, using the data included in the R Markdown file.

```{r problem_4_data,include=FALSE}

#####DO NOT MODIFY THIS CHUNK

set.seed(5678)
var1<-rnorm(10,25,5)
names<-letters[1:10]

dat4<-tibble(names,var1)
```

```{r problem_4,echo=FALSE}

# Create the dot plot with horizontal lines
ggplot(dat4, aes(x = var1, y = names)) +
  geom_point(color = "black", size = 4) +  # Black dots
  geom_vline(xintercept = 0, linetype = "dotted", color = "red") +  # Dotted vertical lines
  labs(x = "var1", y = "names") +
  theme_minimal() +
  theme(
    panel.grid.major.y = element_line(color = "red", linetype = "dotted"),  # Red dotted lines
    axis.text.y = element_text(size = 12),  # Adjust y-axis text size
    axis.title = element_text(size = 14)  # Increase axis title size for clarity
  )
```

## Problem 5

Create the figure in the solution for Problem 5, using the data included in the R Markdown file.

```{r problem_5_data,include=FALSE}

#####DO NOT MODIFY THIS CHUNK

set.seed(13)
var1<-rnorm(10,25,5)
names<-letters[1:10]

dat5<-tibble(names,var1)
```

```{r problem_5,echo=FALSE}


# Create the dot plot with vertical lines, adjusted for axis swap
ggplot(dat5, aes(x = names, y = var1)) +
  geom_point(color = "darkgreen", size = 4) +  # Green dots
  geom_segment(aes(x = names, xend = names, y = 0, yend = var1), color = "darkgreen") +  # Vertical lines
  labs(x = "Category", y = "Variable 1") +
  theme_minimal() +
  theme(
    axis.text.x = element_text(size = 12),  # Adjust x-axis text size
    axis.title = element_text(size = 14)  # Increase axis title size for clarity
  )


```

## Problem 6

Create the figure in the solution for Problem 6, using the data included in the R Markdown file.

```{r problem_6_data,include=FALSE}

#####DO NOT MODIFY THIS CHUNK

set.seed(8)
fiction<-tibble(Genre=rep("Fiction",5),Time=seq(1:5),Total=sample(1:10,5))
set.seed(7)
biography<-tibble(Genre=rep("Biography",5),Time=seq(1:5),Total=sample(1:10,5))
set.seed(9)
mystery<-tibble(Genre=rep("Mystery",5),Time=seq(1:5),Total=sample(1:10,5))

books_checked_out<-bind_rows(fiction,biography,mystery)
```

```{r problem_6,echo=FALSE}

# Create the stacked area plot
ggplot(books_checked_out, aes(x = Time, y = Total, fill = Genre)) +
  geom_area() +
  labs(x = "Time", y = "Total", title = "Books Checked Out") +
  scale_fill_manual(values = c("red", "green", "blue")) +  # Custom colors for each genre
  theme_minimal() +
  theme(
    axis.title = element_text(size = 14),  # Increase axis title size
    axis.text = element_text(size = 12),  # Adjust axis text size
    legend.title = element_text(size = 14),  # Increase legend title size
    legend.text = element_text(size = 12)  # Adjust legend text size
  )

```

## Problem 7

Create the figure in the solution for Problem 7, using the data included in the R Markdown file.

```{r problem_7_data,include=FALSE}

#####DO NOT MODIFY THIS CHUNK

books_checked_out2 <- books_checked_out %>%
  filter(Time==1 | Time==5) %>%
  pivot_wider(names_from = Time,values_from=Total) %>%
  rename(Time1=`1`,Time5=`5`)
```
   
```{r,problem_7,echo=FALSE,message=FALSE}   
# Create the plot
ggplot(books_checked_out2, aes(x = Time1, y = Genre)) +
  geom_point(color = "red", size = 4) +  # Red dots for Time 1
  geom_point(aes(x = Time5), color = "purple", size = 4) +  # Purple dots for Time 5
  geom_segment(aes(x = Time1, xend = Time5, y = Genre, yend = Genre), color = "black") +  # Black lines connecting the dots
  labs(x = "Total", y = "Genre", title = "Books Checked Out") +
  theme_minimal() +
  theme(
    axis.text.y = element_text(size = 12),  # Adjust y-axis text size
    axis.title = element_text(size = 14),  # Increase axis title size
    legend.position = "none"  # Remove legend since we have custom colors for each point
  )

```

## Problem 8

Create the figure in the solution for Problem 8, using the data included in the R Markdown file.

```{r, problem_8_data,include=FALSE}

pie_dat<-c(1,2,3,4,5)
```

```{r, problem_8,echo=FALSE}
###HINT: check the Help file for pie to see how to specify the color to the my_color palette

library(RColorBrewer)

# Color palette
my_color <- brewer.pal(5, "Spectral")

# Create the pie chart
ggplot(data.frame(x = pie_dat), aes(x = "", y = x, fill = factor(1:length(x)))) +
  geom_bar(stat = "identity", width = 1) +
  coord_polar(theta = "y") +  # Make it a pie chart
  scale_fill_manual(values = my_color) +  # Custom colors
  theme_void() +  # Remove the axes and gridlines
  labs(title = "Total")

```


