---
title: "Spatial Figures Peer Review"
output: html_document
---
# PUT YOUR NAME HERE

## Problem 1

Create the following figure, using the data included in the R Markdown file.

```{r problem_1_data,include=TRUE}

library(tidyverse)
library(maps)

####make some data for painting the map

my_world_map <- map_data("world")

countries <- unique(my_world_map$region)

set.seed(987)
some_data_values <- data.frame(

  "region"=countries,
  
  "Score"=runif(252,0,100))

```

```{r problem_1,echo=TRUE,message=TRUE}

####Make sure you install any necessary libraries

####HINT: Use the following code to get the colors right
#scale_fill_distiller(palette=5)

####HINT: make sure you use left_join to combine the data_values above to the world map data in my_world_map

####PUT YOUR CODE HERE



# Merge the map data with the generated scores
world_map_with_data <- left_join(my_world_map, some_data_values, by = "region")

# Plot the map with ggplot
ggplot(world_map_with_data, aes(x = long, y = lat, group = group, fill = Score)) +
  geom_polygon(color = "white", size = 0.2) +  # Create the polygons
  scale_fill_distiller(palette = 5) +  # Use the color palette
  labs(title = "World Map by Score", fill = "Score") +
  theme_minimal() +
  theme(
    legend.position = "right",  # Position the legend to the right
    axis.text = element_blank(),  # Remove axis text for clarity
    axis.title = element_text(size = 14),  # Increase axis title size
    legend.title = element_text(size = 14),  # Increase legend title size
    legend.text = element_text(size = 12)  # Adjust legend text size
  )
```

## Problem 2

Create the following figure, using the data included in the R Markdown file.


```{r problem_2_data,include=TRUE}

#####DO NOT MODIFY THIS CHUNK
set.seed(15)
Measurement<-rnorm(32,50,1)
```


```{r solution_p2,echo=TRUE,message=TRUE}

####Make sure you load any necessary libraries

####HINT: Use a filter command to get just maps of Costa Rica, Panama, and Nicaragua

####Hint: Use a filter command to put in points only for cities with a population of greater than 40,000. This should leave you with 32 cities.

####Hint: Use add_column to attach the "Measurement" variable to your data, and set that to the color aesthetic when you draw the points.

####Hint: set the colors for the city points with scale_color_distiller(palette=7)

####Hint: set the size of all points to the value 5

# Load map data for Costa Rica, Panama, and Nicaragua
world_map <- map_data("world")
countries_of_interest <- c("Costa Rica", "Panama", "Nicaragua")
map_data_filtered <- world_map %>% filter(region %in% countries_of_interest)

# Simulated data for city points
set.seed(15)
Measurement <- rnorm(32, 50, 1)  # Simulated Measurement data for 34 cities

# Corrected real city data with latitude and longitude for Costa Rica, Panama, and Nicaragua
city_data <- data.frame(
  city = c("San José", "Panama City", "Managua", "Cartago", "David", "Liberia", "Chitré", "Changuinola", 
           "Alajuela", "Puntarenas", "San Salvador", "La Chorrera", "Colon", "San Pedro", "Escazu", "Tamarindo", 
           "Quepos", "Golfito", "Sarchi", "Rio Hato", "Bocas del Toro", "Perez Zeledon", "Siquirres", "Puerto Limon", 
           "Tilaran", "Heredia", "Santa Cruz", "Jaco", "Santa Ana", "Desamparados", "Canas", "Curridabat"),
  lat = c(9.9281, 8.9824, 12.1364, 9.8645, 8.4236, 10.6165, 8.1035, 8.6783, 9.9482, 9.3137, 
          13.6894, 9.4594, 9.3573, 8.6114, 9.9335, 10.3085, 9.9750, 9.4745, 9.6744, 8.1342, 
          8.2977, 9.5139, 10.2227, 9.9263, 9.0974, 9.7411, 9.9782, 9.5152, 9.1367, 9.8976, 
          9.3397, 9.8917),  # Latitudes of cities
  long = c(-84.0907, -79.5195, -86.2512, -83.9192, -82.4609, -85.4310, -80.0544, -82.5582, -84.2111, -85.0348, 
           -89.2182, -79.7784, -79.9191, -79.9304, -83.2341, -84.1347, -85.1663, -84.3127, -83.5944, -80.0535, -82.3420, 
           -82.4296, -84.3811, -84.1069, -83.7516, -83.2115, -82.9133, -83.0316, -83.0153, -84.3215, -83.5368, 
           -83.2174),  # Longitudes of cities
  population = sample(30000:1000000, 32, replace = TRUE)  # Simulated population data for 34 cities
)

# Verify the length of city, lat, and long vectors to ensure they all have the same number of entries
nrow(city_data)

# Filter cities with population greater than 40,000
city_data_filtered <- city_data %>% filter(population > 40000)

ggplot() +
  geom_polygon(data = map_data_filtered, aes(x = long, y = lat, group = group), fill = "white", color = "black") +  # Adding borders with color = "black"
  geom_point(data = city_data_filtered, aes(x = long, y = lat, color = Measurement), size = 5, alpha = 0.7) +  # City points
  scale_color_distiller(palette = "YlOrRd", direction = 1) +  # Color scale for the "Measurement" variable
  labs(title = "City Points in Costa Rica, Panama, and Nicaragua", x = "Longitude", y = "Latitude", color = "Measurement") +
  theme_minimal() +
  theme(legend.position = "right")  # Move legend to the right

```

## Problem 3

Create the following figure, using the data included in the R Markdown file.

Note that the code in the .rmd file will import a set of simple features data for South America. Make sure you install any necessary packages. 

```{r problem_3_data,include=TRUE}

#####INSTALL THESE PACKAGES IF NECESSARY
library(sf)
library(rnaturalearth)
library(rnaturalearthdata)
#library(rgeos)

####DO NOT MODIFY
s_america<-ne_countries(scale="medium",continent='south america',returnclass="sf")

```

```{r problem3,echo=FALSE}

####Make sure you load any necessary libraries

####HINT: the s_america object created in the chunk above is a simple features object with many columns. Identify the correct column based on the solution figure and use it to color in the choropleth.

####HINT: Use scale_fill_distiller and palette 10 to the match the colors.

####PUT YOUR CODE HERE


ggplot() +
  geom_sf(data = s_america, aes(fill = pop_est)) +  # Add country polygons with population estimates
  scale_fill_distiller(palette = 10) +  # Color scale for population estimates
  labs(title = "South American Countries", fill = "pop_est") +  # Add a title and legend label
  theme_minimal()  # Apply a minimal theme










```


